Building a GNU/Hurd Cluster

### 2018-01-26 slides/rpctrace.tex
slides - update elisp code to modify \only macros (now runs, but is buggy)

@@

\begin{comment}
    (defun increment-number-at-point ()
      (interactive)
      (skip-chars-backward ``0-9'')
      (or (looking-at ``[0-9]+'')
          (error ``No number at point''))
      (replace-match (number-to-string (1+ (string-to-number (match-string 0))))))

(when (string-match ``[ \t]*$'' test-str)
    (message (concat ``[`` (replace-match " nil nil test-str) ``]'')))

     (while (re-search-forward ``foo[ \t]+bar'' nil t)
       (replace-match ``foobar''))

(defun ff ()
  "increment numbers in string"
  (let (mystr start)
    (setq str (match-string 0)
    (setq start 0)
    (while (string-match "[0-9]+" mystr start)
      (replace-match (number-to-string (1+ (string-to-number (match-string 0)))) nil nil (match-string 0))
  (replace-regexp-in-string ``_'' `` `` (match-string 1))
)

>>>>

\begin{comment}

;; ELISP code to insert and remove slides from beamer \only macros
;;
;; XXX still have to deal with case where \only<2> needs to become \only<2-3> (inserting new frame 3)
;;     or \only<5> has to become \only<0> (deleting frame 5)

(defun incr-only-func (min)
  "increment all numbers in string greater than or equal to a minimum value"
  (let ((mystr (match-string 0)) (start 0) value)
       (save-match-data (while (string-match "[0-9]+" mystr start)
                               (setq value (string-to-number (match-string 0 mystr)))
                               (when (>= value min)
                                     (setq mystr (replace-match (number-to-string (1+ value))
                                                                nil nil mystr)))
                               (string-match "[0-9]+" mystr start)
                               (setq start (match-end 0))))
       mystr))

(defun incr-only (min)
  "increment an only macro"
  (interactive "NSlide number to insert: ")
  (query-replace-regexp "\\only<[^>]+>" `(replace-eval-replacement replace-quote (incr-only-func ,min))))

(defun decr-only-func (min)
  "decrement all numbers in string greater than a minimum value"
  (let ((mystr (match-string 0)) (start 0) value)
       (save-match-data (while (string-match "[0-9]+" mystr start)
                               (setq value (string-to-number (match-string 0 mystr)))
                               (when (> value min)
                                     (setq mystr (replace-match (number-to-string (1- value))
                                                                nil nil mystr)))
                               (string-match "[0-9]+" mystr start)
                               (setq start (match-end 0))))
       mystr))

(defun decr-only (min)
  "decrement an only macro"
  (interactive "NSlide number to remove: ")
  (query-replace-regexp "\\only<[^>]+>" `(replace-eval-replacement replace-quote (decr-only-func ,min))))

@@
